Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-01 reviews/response.Rmd

A2. We have used the term "pair" instead "grouping" to avoid conflict with the definition of "groups into" and rephrased the sentence.

Q3. What is the definition of aperiodic linear granularities? On Page 11, Definition 10, $M_i$ are aperiodic linear granularities. If $M_i$ are aperiodic, then is $M$ also an aperiodic linear granularity? What is the relationship between aperiodic linear granularity and aperiodic
cyclic granularity?

A3. Aperiodic linear granularities are those that can not be defined by Definition 6. If $M_i$ is periodic, then $M = \bigcup M_i$ is periodic, but if each $M_i$'s are aperiodic, then $M$ could be periodic or aperiodic. In Definition 10, we want $M$ to be aperiodic. Definition 10 and introduction of Section 3.3 briefly rephrased to improve clarity.

Q4. $w$ in $T_w$ is not well defined for circular granularities in Section 3.2 & 3.5. The definition of $T_w$ uses $T_w$ itself in the formula making it hard to understand. Relevantly, what is the interpretation of $k$ where $w = 0, 1, \dots k-1$? In my opinion, the number of cycles
should be defined for cyclic granularities, for example, $w_{B,G}(z) = \lfloor z/P(B;G) \rfloor$, which
represent the cycle that the granule is in.

@@

Q7. Page 14, Lines 26-27. Is z the original index for the bottom granularity? If yes, why $C_{katun, baktun}(z) = \lfloor 18 × 20 × z/20 \rfloor mod 20$? Shouldn't it be $z mod 20$? If not, then what is $z$? By Definition 8, $z \in Z$ is the original time index based on the bottom granularity, but here $z$ seems to be defined as the time index based on granularity katun.

A7. $z$ is the original index for the bottom granularity $kin$. The equation is modified since we removed the line expressing the multiple-order-up granularities in terms of $z$. The point is to show how the value of a multiple-order-up granularity can be obtained when values of single-order-up granularities are available. It is sufficient to know the values of the single order-up-granularities at $z$ and not the exact value of $z$, so we chose to not expand it using $z$.

Q8.  Page 11, lines 22-33. The explanation of Figure 3 is confusing. If the week-of-the- semester week type is a quasi-circular granularity, then the day-of-the-semester week type can be also quasi-circular granularity, as all days are nested in weeks. Actually the notation should not be "week-of-the-semester week type", but "semester week-of-the- semester week type". The relationship between G and H should be clarified. It will be clearer if the authors can make a granularity "semester day" (U) from B. Therefore we have the following granularities.
*$Q_{H,M}$ : quasi-circular granularity, 
semester week -of-the-semester week type
*$Q_{U,M}$ : quasi-circular granularity, semester day-of-the-semester week type.

A8. Sem week is removed and only "semester day" abbreviated as "sem day" is introduced. "Day"($B$) and "Sem day"($B'$) differs in their structure as granules of $B'$ corresponds to semesters only. "Stage" is used instead of "Semester week type" to refer to different stages of a semester. Then $A_{B,M}$ is aperiodic, whereas $Q_{B', M}$ is quasi-periodic.

### 2021-05-01 main.Rmd
minor changes

Granularities can also be periodic with respect to other granularities, except for a finite number of periods where they behave in an anomalous way; these are called **quasi-periodic** relationships [@Bettini2000-vy]. In a Gregorian calendar with leap years, day groups quasi-periodically into month with the exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.

@@

Aperiodic linear granularities are those that cannot be specified as a periodic repetition of a pattern of granules as described in Definition \ref{def:periodic}. Aperiodic cyclic granularities capture repetitions of these aperiodic linear granularities.
Examples include public holidays which repeat every year, but there is no reasonably small period within which their behavior remains constant. A classic example is Easter (in the western tradition) whose dates repeat only after 5.7 million years [@Reingold2001-kf]. In Australia, if a standard public holiday falls on a weekend, a substitute public holiday will sometimes be observed on the first non-weekend day (usually Monday) after the weekend. Examples of aperiodic granularity may also include school holidays or a scheduled event. All of these are recurring events, but with non-periodic patterns. Consequently, $P_i$ (as given in \autoref{tab:quasi}) are essentially infinite for aperiodic granularities.

@@

(ref:aperiodic-example) Quasi-circular and aperiodic cyclic granularities illustrated through (a) linear and (b) stacked displays of time. The linear display shows granularities days, weeks, semester days, and stages of a semester distributed over linear time. Here a semester lasts for 18 weeks and 2 days, each consisting of 5 stages. It starts with an orientation stage, followed by a first stage of in-session period (6 weeks), a break (1 week), a second stage of in-session period (7 weeks), a 1-week study break stage, before final exams stage which continue for 16 days. This distribution of semester days within a semester remains the same for every semesters and hence $Q_{B', M}$ with $P$ = 128 days will be a quasi-circular granularity with repeating patterns. $A_{B, M}$ will be an aperiodic cyclic granularity since 
the placement of the semester within an year varies across years and there is no definite number of days after which the semester begins every year.

For example, consider the school semester shown in \autoref{fig:aperiodic-example}. Let the linear granularities $M_1$ and $M_2$ denote the teaching and non-teaching stages of the semester respectively. Both $M_1$, $M_2$ and $M = M_{1}\bigcup M_{2}$ denoting the "stages" of the semester are aperiodic with respect to days ($B$) or weeks ($G$). Hence $A_{B, M}$ denoting day-of-the-stage would be an aperiodic cyclic granularity, because the placement of the semester within an year would vary across years. Here, $Q_{B', M}$ denoting semester-day-of-the-stage would be a quasi-circular granularity since the distribution of semester days within a semester is assumed to remain constant over years.

>>>>

Granularities can also be periodic with respect to other granularities, _"except for a finite span of time where they behave in an anomalous way"_; these are called **quasi-periodic** relationships [@Bettini2000-vy]. In a Gregorian calendar with leap years, day groups quasi-periodically into month with the exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.

@@

Aperiodic linear granularities are those that cannot be specified as a periodic repetition of a pattern of granules as described in Definition \ref{def:periodic}. Aperiodic cyclic granularities capture repetitions of these aperiodic linear granularities.
Examples include public holidays which repeat every year, but there is no reasonably small span of time within which their behavior remains constant. A classic example is Easter (in the western tradition) whose dates repeat only after 5.7 million years [@Reingold2001-kf]. In Australia, if a standard public holiday falls on a weekend, a substitute public holiday will sometimes be observed on the first non-weekend day (usually Monday) after the weekend. Examples of aperiodic granularity may also include school holidays or a scheduled event. All of these are recurring events, but with non-periodic patterns. Consequently, $P_i$ (as given in \autoref{tab:quasi}) are essentially infinite for aperiodic granularities.

@@

(ref:aperiodic-example) Quasi-circular and aperiodic cyclic granularities illustrated through (a) linear and (b) stacked displays of time. The linear display shows granularities days ($B$), weeks ($G$), semester days ($B'$), and stages of a semester ($M$) distributed over linear time. Granules of $B'$ is only defined for days when the semester is running. Here a semester lasts for 18 weeks and 2 days, each consisting of 5 stages. It starts with an orientation stage, followed by a first stage of in-session period (6 weeks), a break (1 week), a second stage of in-session period (7 weeks), a 1-week study break stage, before final exams stage which continue for 16 days. This distribution of semester days within a semester remains the same for every semesters and hence $Q_{B', M}$ with $P$ = 128 days will be a quasi-circular granularity with repeating patterns. $A_{B, M}$ will be an aperiodic cyclic granularity since 
the placement of the semester within an year varies across years and there is no definite number of days after which the semester begins every year.

The linear display shows granularities days ($B$), weeks ($G$), , and stages of a semester ($M$) distributed over linear time.

For example, consider the school semester shown in \autoref{fig:aperiodic-example}. Let the linear granularities $M_1$ and $M_2$ denote the teaching and non-teaching stages of the semester respectively. Both $M_1$, $M_2$ and $M = M_{1}\bigcup M_{2}$ denoting the "stages" of the semester are aperiodic with respect to days ($B$) or weeks ($G$). Hence $A_{B, M}$ denoting day-of-the-stage would be an aperiodic cyclic granularity, because the placement of the semester within an year would vary across years. Here, $Q_{B', M}$ denoting semester-day-of-the-stage would be a quasi-circular granularity 
since the distribution of semester days within a semester is assumed to remain constant over years. Here semester-day is denoted by "sem day" ($B'$) and its granules are only defined for the span of the semesters.
